Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2022-01-25 edubots_surveys.Rnw
Addressing some typos

\begin{abstract} % abstract
Introducing new technologies such as messaging platforms, and the chatbots
attached to them, in higher education, is rapidly growing. This introduction
entails a careful consideration of the potential opportunities and/or challenges
of adopting these tools. Hence, a thorough examination of the teachers’
experiences in this discipline can shed the light on the effective ways of
enhancing students’ learning and boosting their progress. In this contribution,
we have surveyed the opinions of tertiary education teachers based mainly in
Spain and Spanish-speaking countries. The focus of these surveys is to collect
teachers’ feedback about their opinions of the introduction of the messaging
platforms and chatbots in their classes, understand their needs and to gather
information about the various educational use cases where these tools are
valuable. In addition, an analysis of how and when teachers’ opinions towards
the use of these tools can vary across gender, experience, and their discipline
of specialisation is presented. The key findings of this study highlight the
factors that can contribute to the advancement of the adoption of messaging
platforms and chatbots in higher education institutions to achieve the desired
learning outcomes.
\end{abstract}

@@

WhatsApp is, at least in most Western countries, the most popular MIM platform
used by educators to \textcolor{blue}{provide} assignments' feedback to students, support course
discussions, and provide learning resources in informal learning settings
\cite{panah2020study}.  Moreover, the use of WhatsApp in higher education could
enhance social presence \cite{tang2017mobile} and foster trust relationships
between educators and students embedded in the social learning process
\cite{gachago2015crossing}; however, this last paper also reflects the need for
learners to ``take ownership of the tool'' and the advantages of social learning
in general. At the same time, it also mentions different challenges, among which
the most important is the blurring of social and academic life. Examining these
opinions will be the objective of RQ3 in this paper.

Nevertheless, there are challenges when using MIM tools that occur due to the
blurring of boundaries between academic and private life. This can lead to
technostress \cite{gachago2015crossing}, difficulty in managing
responsibilities, especially among mature students, and lack of privacy
\cite{tang2017mobile}.  Students' dropout of the MIM groups, as they can leave
groups at any time, can hinder their learning and undermine educators' efforts
\cite{mwakapina2016whatsapp}.  In addition, there is a need to set rules and
norms for these MIM groups in order to maintain the safety of these online
communities for students \cite{abbas2021onlinechat}. However, these rules should
not affect students' ownership and control, since it is vital to advance in
their learning \cite{gachago2015crossing} process.  This is why examining the
role of MIM in higher education is still a challenge, and why the opinions of
the teaching community towards them have to be examined, as we do in this paper.

>>>>

\begin{abstract} % abstract
Introducing new technologies such as messaging platforms, and the chatbots
attached to them, in higher education, is rapidly growing. This introduction
entails a careful consideration of the potential opportunities and/or challenges
of adopting these tools. Hence, a thorough examination of the teachers’
experiences in this discipline can shed light on the effective ways of
enhancing students’ learning and boosting their progress. In this contribution,
we have surveyed the opinions of tertiary education teachers based in
Spain (mainly) and Spanish-speaking countries. The focus of these surveys is to collect
teachers’ feedback about their opinions regarding the introduction of the messaging
platforms and chatbots in their classes, understand their needs and to gather
information about the various educational use cases where these tools are
valuable. In addition, an analysis of how and when teachers’ opinions towards
the use of these tools can vary across gender, experience, and their discipline
of specialisation is presented. The key findings of this study highlight the
factors that can contribute to the advancement of the adoption of messaging
platforms and chatbots in higher education institutions to achieve the desired
learning outcomes.
\end{abstract}

@@

WhatsApp is, at least in most Western countries, the most popular MIM platform
used by educators to \textcolor{blue}{provide} assignments' feedback to students, support course
discussions, and provide learning resources in informal learning settings
\cite{panah2020study}.  Moreover, the use of WhatsApp in higher education could
enhance social presence \cite{tang2017mobile} and foster trust relationships
between educators and students embedded in the social learning process
\cite{gachago2015crossing}; however, this last paper also reflects the need for
learners to ``take ownership of the tool'' and the advantages of social learning
in general. At the same time, it also mentions different challenges, among which
the most important is the blurring of social and academic life; indeed, there are challenges when using MIM tools that occur due to the
blurring of boundaries between academic and private life. This can lead to
technostress \cite{gachago2015crossing}, difficulty in managing
responsibilities, especially among mature students, and lack of privacy
\cite{tang2017mobile}.  Students' dropout of the MIM groups, as they can leave
groups at any time, can hinder their learning and undermine educators' efforts
\cite{mwakapina2016whatsapp}.  In addition, there is a need to set rules and
norms for these MIM groups in order to maintain the safety of these online
communities for students \cite{abbas2021onlinechat}. However, these rules should
not affect students' ownership and control, since it is vital to advance in
their learning \cite{gachago2015crossing} process.  This is why examining the
role of MIM in higher education is still a challenge, and why the opinions of
the teaching community towards them have to be examined, as we do in this paper.
